### 2024-05-19 Paper/MSEPM-ManuscriptSupplement.tex
Manuscript revision

\large{\bf{The Multi-State Epigenetic Pacemaker enables the 
identification of combinations of factors that influence DNA methylation - Supplementary Information}}\\ \\
\noindent{\small Colin Farrell$^{1,3}$, Kalsuda Lapborisuth$^{1}$, 
                 Sagi Snir$^{2}$,\\ and Matteo Pellegrini$^{1,3}$\\ \\
\noindent{\footnotesize 
$^1$Dept. of Molecular, Cell and Developmental Biology; \\ University of
California, Los Angeles, CA 90095, USA;;\\
\noindent
$^2$Dept. of Evolutionary Biology, University of  Haifa, Israel;\\
$^3$Corresponding Authors; colinpatfarrell@g.ucla.edu, matteop@mcdb.ucla.edu 
}

>>>>

\large{\bf{The Multi-State Epigenetic Pacemaker enables the 
identification of combinations of factors that influence DNA methylation - Supplementary Information}}\\ \\
\noindent{\small Colin Farrell$^{1,4}$, Keshiv Tandon ${1}$, Roberto Ferrari$^{2}$, Kalsuda Lapborisuth$^{1}$, 
                 Sagi Snir$^{3}$,\\ and Matteo Pellegrini$^{1,4}$\\ \\
\noindent{\footnotesize 
$^1$Dept. of Molecular, Cell and Developmental Biology; \\ University of
California, Los Angeles, CA 90095, USA;;\\
\noindent
$^2$Dept. of Chemistry, Life Sciences and Environmental Sustainability, Laboratory of Molecular Cell Biology of the Epigenome (MCBE), University of Parma, Italy;\\
$^3$Dept. of Evolutionary Biology, University of  Haifa, Israel;\\
$^4$Corresponding Authors; colinpfarrell@gmail.com, matteop@mcdb.ucla.edu 
}
